### 2019-03-08 manuscript/Notation.Rnw
Pushing notation.pdf

\documentclass{article}
\usepackage{amssymb}
\begin{document}

\section{Introduction}
KAJAL's (and grady) Lit review

@@

Consider the curve $C_j^m: \mathbb{S} \rightarrow \mathbb{R}^2, j = 1, \dots, n_m$ which is only observe on some region (don't want to use R here...) $S_j \subset \mathbb{S}$.  The goal here is to impute the missing part of each shape.  Then perform some type of complete shape analysis.

\section{Notation}
% $$
% C: [0,1] \rightarrow \mathbb{R}^2 \times \left\{0,1\right\}^2
% $$
$$
C: \mathbb{S} \rightarrow \mathbb{R}^2 
$$
In general, we have a missingness function like this.  This allows for us to be missing the $x$ or $y$ value individually at a given point along the curve.  We aren't really going to deal with that case here so we are dealing with something a little more specific.  
$$
R: \mathbb{S} \rightarrow \left\{0,1\right\}^2
$$
We are really dealing with this:  
$$
R: \mathbb{S} \rightarrow \left\{\{0,0\},\{1,1\}\right\}
$$
This means that at any given location that we are missing a value, both the $x$ and $y$ values are missing.

Here $R$ is a missingness indicator function.  It is 1 when the value of $C$ is unobserved and 0 otherwise. \\

The set of fully observed shapes is the set $\mathcal{C}^o$ and contains $n_o$ shapes; the set of partially observed shapes is the set $\mathcal{C}^m$ and contains $n_m$ shapes.  Together $(\mathcal{C}^o,\mathcal{C}^m) = \mathcal{C}$ \\

Next we want to consider the joint distribution of the curves with the missingnes indicator.  
$$
P(C, R) = P(C_{obs}, C_{mis}, R)
$$

Bayesian approach: 
Construct a model for 
$$
P(C_{obs}, C_{mis}, R | \theta, \phi)
$$
where $\theta$ is a vector of parameters associated with modeling the data and $\phi$ are parameters associated with the model of the missing data mechanism.

@@

%\cite{deRuiter2008}
%\bibliographystyle{chicago}
%\bibliography{shapebib}

>>>>

\documentclass{article}
% This is the recommended preamble for your document.
\usepackage{setspace}
\usepackage{url}
%% Load De Gruyter specific settings 
\usepackage{dgjournal}          
\usepackage{color,soul}
%% The mathptmx package is recommended for Times compatible math symbols.
%% Use mtpro2 or mathtime instead of mathptmx if you have the commercially
%% available MathTime fonts.
%% Other options are txfonts (free) or belleek (free) or TM-Math (commercial)
\usepackage{amssymb,amsmath}
\usepackage{multirow}
%% Use the graphics package to include figures
\usepackage{graphics}
%% Use natbib with these recommended options
\usepackage[authoryear,comma,longnamesfirst,sectionbib]{natbib} 
\usepackage{lscape}
\newcommand{\hlc}[2][yellow]{{\sethlcolor{#1}\hl{#2}}}
\setstretch{1}
\setlength{\bibsep}{10pt}
\usepackage{booktabs}

\usepackage{subfigure}% Support for small, `sub' figures and tables. Your choice of alternative may be preferred instead.
\usepackage{color,soul}
\usepackage{moreverb}
\usepackage{graphicx}
\usepackage[table]{xcolor}

\begin{document}
\section{Introduction}
KAJAL's (and grady) Lit review

@@

%Consider the curve $C_j^m: \mathbb{S} \rightarrow \mathbb{R}^2, j = 1, \dots, n_m$ which is only observe on some region (don't want to use R here...) $S_j \subset \mathbb{S}$.  The goal here is to impute the missing part of each shape.  Then perform some type of complete shape analysis.

\section{Notation}
% $$
% C: [0,1] \rightarrow \mathbb{R}^2 \times \left\{0,1\right\}^2
% $$
Consider a closed curve, $C$, in two dimensions: 
$$
C: \mathbb{S} \rightarrow \mathbb{R}^2 
$$.

Since, shapes should be invariant across several transformations including translation, scaling, rotation, and reparameterizaion, the shape $C$ is defined to be the equivalence class

$$
C = \{\sigma O C(\gamma(t)) + a, \gamma \in \Gamma, O \in SO(2), a\in \mathcal{R}^2, \sigma > 0\} 
$$.

Consider a set of shapes $\mathcal{C}$, containing some fully observed shapes and some partially observed shapes.  We define the set of fully observed shapes to be called 
$$
\mathcal{C}^o = (C^o_1 \cdots C^o_{n_o})
$$

whereas the set of partially observed shapes is the referred to as

$$
\mathcal{C}^m = (C^m_1 \cdots C^m_{n_m})
$$.

Each $C^m_j$ consists of a the observed part $C^m_{j,obs}$ and the missing part $C^m_{j,mis}$ such that $C^m_j = (C^m_{j,obs},C^m_{j,mis})$.  That is

$$
C^m_{j,mis} = C_j: [a,b] \rightarrow \mathbb{R}^2
$$
where
$$
[a,b] = {x \in \mathcal{S} | R'_j(x) = 1}
$$.

So

$$
\mathcal{C}^m_{obs} = (C^m_{1,obs} \cdots C^m_{n_m,obs})
$$

and

$$
\mathcal{C}^m_{mis} = (C^m_{1,mis} \cdots C^m_{n_m,mis})
$$

We then have

$$
\mathcal{C} = (\mathcal{C}^o,\mathcal{C}^m) = (\mathcal{C}^o,\mathcal{C}^m_{mis},\mathcal{C}^m_{obs})
$$

and $n = n_o + n_m$. \\

In traditional missing data settings, a missingness indicator is defined such that it is 1 when a data point is missing and 0 otherwise.  In this setting we define a function indicating which part of the function is observed and which is missing.  This function is called $R$ and is defined as follows:

$$
R: \mathbb{S} \rightarrow \left\{0,1\right\}^2
$$

While this function allows for a curve to be missing the $x$ or $y$ value individually at a given point in $\mathbb{S}$, in our setting both the $x$ and $y$ values are either both observed or both missing, and the indicator function in our setting is defined as follows:

$$
R': \mathbb{S} \rightarrow \left\{\{0,0\},\{1,1\}\right\}
$$

We will work with $R'$ as a missingness indicator function here, and it is 1 when the values of $(x(t),y(t))$ are both unobserved and 0 if both $(x(t),y(t))$ are observed where $t \in \mathbb{S}$.  The set of all missingness functions is defined to be $\mathcal{R} = (R'_1, \cdots, R'_n)$.     \\

Next, we want to consider the joint distribution of the set of curves $\mathcal{C}$ and the set of missingness indicator functions $\mathcal{R}$.

%How do I say this: However, since the shape spaces that we are interested in this context are non-linear and infinite dimensional we need to take care when defining a probability density function over this space.  Specifically we are interested in defining this density function over a manifold $M = \mathbb{S}$ as opposed to the manifold that is used in traditional statistical settings: $M = \mathbb{R}^n$.

Next we want to consider the joint distribution of the curves with the missingnes indicator.

$$
P(\mathcal{C}, \mathcal{R}) = P(\mathcal{C}^o, \mathcal{C}^m_{mis}, \mathcal{C}^m_{obs}, \mathcal{R})
$$

In order to perform imputations we first need to define a model for the likelihood:

$$
P(\mathcal{C}^o, \mathcal{C}^m_{mis}, \mathcal{C}^m_{obs}, \mathcal{R}| \theta, \phi)
$$

where $\theta$ is a vector of parameters associated with modeling the data (i.e. $\mathcal{C}$) and $\phi$ are parameters associated with the model of the missing data mechanism (i.e. $\mathcal{R}'$).

We can then place a prior distribution on the parameters $p(\theta, \phi)$ which will lead to a posterior probability:

$$
P( \theta, \phi|\mathcal{C}^o, \mathcal{C}^m_{mis}, \mathcal{C}^m_{obs}, \mathcal{R})\propto P(\mathcal{C}^o, \mathcal{C}^m_{mis}, \mathcal{C}^m_{obs}, \mathcal{R}| \theta, \phi) \times p(\theta, \phi)
$$

@@

\citet{deRuiter2008}
\bibliographystyle{chicago}
\bibliography{shapebib}
